---
title: "assignment1"
author: "Ketan P Pise"
date: "18 September 2020"
output: html_document
---

```{r setup, include=FALSE, echo = TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reproducibal Research Assignment
### Introduction 
In this assignment we will use data from personal activity monitoring device.

##Importing file and necessary library
1.Importing necessary library as well as importing data is first task of any application.

```{r import, echo=TRUE}
df <- read.table("activity.csv", sep = ',', header = TRUE, colClasses = c("numeric", "Date", "integer"))
head(df)
```

##2. constructing plot using histogram

```{r }
library(dplyr)
library(ggplot2)
data <- df %>% filter(!is.na(steps)) %>% group_by(date) %>% summarize(steps = sum(steps)) %>% print
```

## plot
```{r plot}
library(ggplot2)
g <- ggplot(data, aes(x = steps))
g + geom_histogram(binwidth = 1000) + labs(title = 'Histogram of Steps per day', x = 'Steps per Day', y = 'Frequency')
```

## 3.Calculating mean and median
Mean and median number of steps taken each day
```{r mean&median}
mean_data <- mean(data$steps, na.rm = TRUE)
median_da <- median(data$steps, na.rm = TRUE)
mean_data
```

```{r}
median_da
```

## 4.Time series plot of the average number of steps taken
```{r interval.data}
time_series <- df %>% filter(!is.na(steps)) %>% group_by(interval) %>% summarize(steps = mean(steps)) %>% print
```
plot
```{r}
plot(time_series$interval, time_series$steps, type = 'l', xlab = 'Interval', ylab = 'steps taken')
```

## 5. The 5-minute interval that, on average, contains the maximum number of steps
```{r}
time_series[which.max(time_series$steps), ]
```


## 6.Code to describe and show a strategy for imputing missing data
Taking mean of steps data and exchanging mean to all NA data
```{r}
data_full <- df
nas <- is.na(data_full$steps)
avg_interval <- tapply(data_full$steps, data_full$interval, mean, na.rm=TRUE, simplify=TRUE)
data_full$steps[nas] <- avg_interval[as.character(data_full$interval[nas])]
head(data_full)
```

## 7.Histogram of the total number of steps taken each day after missing values are imputed
```{r}
data_step <- data_full %>% group_by(date) %>% summarize(steps = sum(steps)) %>% print
g <- ggplot(data_step, aes(steps))
g + geom_histogram(binwidth = 1000) + xlab('steps taken')
```

## 8.Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

Staterging on all weekdays and weekend days as 6 days weekdays later weekend days
```{r}
data_full$dayType<- ifelse(as.POSIXlt(data_full$date)$wday %in% c(0,6), "weekends","weekdays")
head(data_full)
```

## 8.1 plot
```{r}
aggre_Data<- aggregate(steps ~ interval + dayType, data=data_full, mean)
ggplot(aggre_Data, aes(color = dayType, interval, steps)) + 
    geom_line() +
    facet_grid(dayType ~ .) +
    xlab("5-Minute Interval") + 
    ylab("steps taken")
```